---
title: "Basic Analysis About Severe Weather Events With exploring the NOOA Storm Database"
author: "Vivien B.W. H"
date: "2015年5月22日"
output: html_document
---

In this document, The basic goal of this assignment is to explore the NOAA Storm Database and answer some basic questions about severe weather events.  

The data analysis mainly focuses on the following questions:

1. Across the United States, which types of events (as indicated in the EVTYPE variable) are most harmful with respect to population health?

2. Across the United States, which types of events have the greatest economic consequences?


**NOTES**: This R Markdown document is encoded using UTF-8. May this information helped if not all of the characters in this document shows themselves well.

## **Data Processing**

```{r}
summary(cars)
```

## **Results**
You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
