---
title: "Basic Analysis About Severe Weather Events With exploring the NOOA Storm Database"
author: "Vivien B.W. H"
date: "2015-5-22"
output: html_document
---
## **Synopsis**
In this document, the NOAA [Storm Database](https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2) is explored and some basic questions about severe weather events are answered.  

Data analysis mainly focuses on the following questions:

1. Across the United States, which types of events (as indicated in the EVTYPE variable) are most harmful with respect to population health?

2. Across the United States, which types of events have the greatest economic consequences?


**NOTES**: This R Markdown document is encoded using UTF-8. May this information helped if not all of the characters in this document shows themselves well.

## **Data Processing**
Load required packages and set timezone.

```{r}
## Required packages
packages <- c("data.table", "xtable", "ggplot2")
sapply(packages, require, character.only=TRUE, quietly=TRUE)

## Set Local Timezone as en_US.UTF-8
Sys.setlocale("LC_TIME", "en_US.UTF-8")
```

### Download raw data and documentation files

Download the storm data documentation files.

* National Weather Service [Storm Data Documentation](https://d396qusza40orc.cloudfront.net/repdata%2Fpeer2_doc%2Fpd01016005curr.pdf)
* National Climatic Data Center Storm Events [FAQ](https://d396qusza40orc.cloudfront.net/repdata%2Fpeer2_doc%2FNCDC%20Storm%20Events-FAQ%20Page.pdf)

```{r downloaddocs, cache=TRUE}
## Check to see if the file exists; if not, make it...
if (!file.exists("StormDataDocumentation.pdf")) {
        file.url<-"https://d396qusza40orc.cloudfront.net/repdata%2Fpeer2_doc%2Fpd01016005curr.pdf"
        download.file(file.url, destfile="StormDataDocumentation.pdf", 
                      method = "curl")
        }

## Check to see if the file exists; if not, make it...
if (!file.exists("StormEventsFAQ.pdf")) {
        file.url<-"https://d396qusza40orc.cloudfront.net/repdata%2Fpeer2_doc%2FNCDC%20Storm%20Events-FAQ%20Page.pdf"
        download.file(file.url, destfile="StormEventsFAQ.pdf", 
                      method = "curl")
        }
```

Download the zipped [Storm Data](https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2) [49Mb].

```{r}
## Check to see if the source data set zip exists; if not, make it...
if (!file.exists("StormData.csv.bz2")) {
        ## Download the zip file and load it into R
        file.url<-'https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2'
        download.file(file.url, destfile="StormData.csv.bz2", 
                      method = "curl")
        }
```

### Load Data into R

Load raw data into R, store it into data table, and take a look.

```{r loaddata, cache=TRUE}
## Read csv file
con <- file.path(getwd(), "StormData.csv.bz2")
dataset <- read.csv(con, stringsAsFactors = FALSE)

## Convert data frame into data table
dataset <- data.table(dataset)

## Take a look
str(dataset)
```

### Clean data
